### 2023-08-01 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
nothing major
yny

Vesicle hydrodynamics in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF}. Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics. In the absence of an osmotic gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{Quaife2021_PRF}. Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after its passage through the strong confinement \cite{Quaife2021_PRF}.  These results imply that the membrane permeability may be inferred from vesicle hydrodynamics under a strong confinement.  Motivated by these results, in this work we seek to investigate how strong confinement may affect the hydrodynamics of a multi-component vesicle? This question is highly relevant to hydrodynamics of cells in a confinement, and to our knowledge has not been well studied.

@@

\todo[inline]{Bryan is here}
We conclude this example by considering the different shapes that
single-component and multicomponent shapes display. Since we have
initialized the lipid species to initially be phase separated, the phase
energy is nearly constant for all cases, and is therefore not plotted.
The tension energy, on the other hand, increases as the vesicle
approaches the neck, but its general shape is similar for all five
cases, and it too is not plotted. However, the bending energies show
different behaviors for each of the cases (Figure~\ref{fig:bendingAll}).
The main difference being that the multicomponent vesicles with a higher
percentage of floppy regions have less bending energy, especially as the
vesicle passes through the neck. We also note that the bending energy
undergoes several transient increases and decreases. These occur when
the tail of the vesicle undergoes transitions from lower energy shapes,
such as `C' or `S' shapes, to high energy shapes, such as 'W' shapes.
Figure~\ref{fig:bendingSC_contracting} shows these different vesicle
shapes for the single-component vesicle and multicomponent vesicle that
is 45\% floppy. The shapes at several critical points along the bending
energy are included, and we can indeed see that transitioning vesicle
shape between these different states.

>>>>

Hydrodynamics of vesicles in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF}. Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics. In the absence of an osmotic gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{Quaife2021_PRF}. Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after its passage through the strong confinement \cite{Quaife2021_PRF}.  These results imply that the membrane permeability may be inferred from vesicle hydrodynamics under a strong confinement.  Motivated by these results, in this work we seek to investigate how strong confinement may affect the hydrodynamics of a multi-component vesicle? This question is highly relevant to hydrodynamics of cells in a confinement, and to our knowledge has not been well studied.

@@

We conclude this example by considering the different shapes that
single-component and multicomponent shapes display. Since we have
initialized the lipid species to initially be phase separated, the phase
energy is nearly constant for all cases, and is therefore not plotted.
The tension energy, on the other hand, increases as the vesicle
approaches the neck, but its general shape is similar for all five
cases, and it too is not plotted. However, the bending energies show
different behaviors for each of the cases (Figure~\ref{fig:bendingAll}).
The main difference being that the multicomponent vesicles with a higher
percentage of floppy regions have less bending energy, especially as the
vesicle passes through the neck. We also note that the bending energy
undergoes several transient increases and decreases. These occur when
the tail of the vesicle undergoes transitions from lower energy shapes,
such as `C' or `S' shapes, to high energy shapes, such as 'W' shapes.
Figure~\ref{fig:bendingSC_contracting} shows these different vesicle
shapes for the single-component vesicle and multicomponent vesicle that
is 45\% floppy. The shapes at several critical points along the bending
energy are included, and we can indeed see that transitioning vesicle
shape between these different states.
